Are We Reusing Outdated Code from Stack Overflow?

### 2016-11-14 cloneoverflow-latex/cloneoverflow.tex
Updated Latex and a few results + diagrams

\subsection{Experimental Framework}
To answer the three research questions, an experimental framework is designed as depicted in \Cref{fig:exp_framework}. We process two datasets, Stack Overflow and open source projects from Qualitas corpus. Java code fragments are extracted from Stack Overflow posts using regular expressions. We pre-process Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection. Then, we deploy two clone detection tools, Simian \cite{simian} and NiCad \cite{Roy2008,Cordy}, to locate clones between the two datasets. Due to a technical limit of Simian and NiCad to scale to large datasets, we partition the input and run the tools multiple times. Each run is composed of the whole Stack Overflow data and a single Qualitas project. We repeat the process until we cover 109 projects.

@@

\subsubsection{Datasets}
\begin{table}
	\centering
	\caption{Stack Overflow and Qualitas datasets}
	\label{tab:datasets}
	\small
	\begin{tabular}{l|r|r}
		\hline 
		Dataset & No. of files & SLOC \\
		\hline
		Stack Overflow & 144,075 & 2,347,269 \\ 
		\hline 
		Qualitas &  138,238 & 16,081,899 \\ 
		\hline 
	\end{tabular} 
\end{table}

@@

\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas} \cite{QualitasCorpus}. It is a curated Java corpus that has been used in several software engineering studies \cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The projects in the corpus represent various domains of software systems ranging from programming language to 3D and visualisation \cite{QualitasCorpus}. We selected the 20130901r snapshot of Qualitas corpus containing 112 Java open source projects. This release contains projects with releases no later than 1st September 2013. We chose a snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow. The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment, January--December 2016. The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow. Out of 112 Qualitas projects, there are 3 projects; \textit{eclipse}, \textit{jre}, and \textit{squirrel-sql}; that do not contain Java source code so they are removed from the study. This results in totally 109 projects analysed in the study. As shown in \Cref{tab:datasets}, the 109 Qualitas project have 138,238 Java files containing 16,081,899 lines of code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

@@

\begin{table}
	\centering
	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian and NiCad}
	\label{tab:raw_stats}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\
			\hline
			Snippets & 1,406 & 1,360 & 1,197 & 12,884 \\
			Total C$_{\textrm{\textit{pairs}}}$ & 54,790 & 59,936,722 & 127,305 & 206,718,663 \\
			Avg.~C$_{\textrm{\textit{pairs}}}$ & 52 & 44,104 & 106 & 16,046 \\
			Avg.~C$_{\textrm{\textit{size}}}$ & 7.45 & 4.81 & 9.54 & 5.31 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 28\% & 29\% & 25\% & 21\% \\
			\hline
		\end{tabular} %
	}
\end{table}

@@

\begin{table}
	\centering
	\caption{No.~of projects in Qualitas successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{l|r|r|r|r}
		\hline
		& Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$  & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ 
		\hline
		\textit{Successful} & 109 & 109 & 97 & 82 \\ 
		\textit{Clust.~fail} & -- & -- & 6 & 16 \\
		\textit{Renm.~fail} & -- &  -- & -- & 11 \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}[H]
	\centering
	\caption{Distribution of agreement-based clone pairs using Bellon's criteria for \textit{df} and \textit{EvCl} settings}
	\label{t_agreed_good_clone_pairs}
	\small
	\begin{tabular}{l|l|r|r}
		\hline
		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c}{No.~of clone pairs} \\
		\hline
		Simian & NiCad & good-match & ok-match \\
		%\hline
		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvCl}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvCl}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		\textit{df} & \textit{df} & 10 	& 3800 \\ 
		\textit{df} & \textit{EvCl} 	& 26 	& 1017 \\ 
		\textit{EvCl} 	& \textit{df} 	& 10 	& 88 \\
		\textit{EvCl} 	& \textit{EvCl} 	& 2228 & 19777 \\ 
		\hline
		\multicolumn{2}{l|}{Total} & 2274 & 24682 \\
		\hline
		\multicolumn{2}{l|}{Total (unique)} & 2261 & 23868 \\
		\hline
	\end{tabular}
\end{table}

\begin{figure*}
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{venn4_pairs_good_pt1+2}
		\caption{Distributions of good-match(0.7) pairs}
		\label{fig:venn4_orig_good}
	\end{minipage}
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{venn4_pairs_ok_pt1+2}
		\caption{Distributions of ok-match(0.7) pairs}
		\label{fig:venn4_orig_ok}
	\end{minipage}
\end{figure*}

@@

\begin{table*}
	\centering
	\caption{Classification results of agreement-based and non agreement-based clone pairs. S$_u$ denotes a number of unique Stack Overflow snippets. Q$_u$ and Q$_{up}$ denote a number of unique Qualitas Java files and unique Qualitas projects respectively.}
	\label{tab:classification_good_o}
	\small
	\resizebox{2.1\columnwidth}{!}{%
	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
		\hline
		Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
		\hline 
		\hline
		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 33  & 8 & \textbf{49} & 12 & 14 & 10 & 4459 & 35 & 82 & \textbf{4576} & 99 & 136 & 29 & \textbf{4625} & 110 & 150 & 33 \\
		\hline 
		\hline 
		%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 35 & 0 & 90 & 8 & \textbf{133} & 68 & 59 & 23 & 13 & 12 & 134 & \textbf{159} & 39 & 72 & 23 & \textbf{292} & 103 & 125 & 31 \\
		%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 36 & 0 & 229 & 3 & \textbf{268} & 76 & 151 & 14 & 169 & 52 & 14 & \textbf{235} & 92 & 119 & 22 & \textbf{503} & 164 & 261 & 24 \\
		\multirow{1}{*}{\textit{Simian$_{df}$}} & 71 & 0 & 318 & 11 & \textbf{401} & 138 & 210 & 37 & 182 & 64 & 148 & \textbf{394} & 120 & 191 & 45 & \textbf{795} & 246 & 386 & 55 \\
		\hline
		%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 5 & 0 & \textbf{9} & 9 & 5 & 4 & 24 & 3 & 78 & \textbf{105} & 41 & 39 & 12 & \textbf{114} & 48 & 44 & 14 \\ 
		%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 0  & 0 & 10 & 0 & \textbf{10} & 7 & 8 & 5 & 6 & 3 & 26 & \textbf{35} & 17 & 16 & 8 & \textbf{45} & 24 & 24 & 9 \\ 
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 15 & 0 & \textbf{19} & 15 & 13 & 9 & 30 & 6 & 104 & \textbf{140} & 51 & 55 & 20 & \textbf{159} & 66 & 68 & 23 \\ 
		\hline
		%		\multirow{1}{*}{\textit{NiCad$_{df}$}*} & 4  & 0 & 1 & 0 & \textbf{5} & 4 & 5 & 3 & 23 & 1 & 67 & \textbf{91} & 28 & 31 & 10 & \textbf{96} & 33 & 37 & 13 \\ 
			%		\hline
	\end{tabular} 
	}
\end{table*}

%\begin{table}
%	\centering
%	\caption{Distribution of classification category A--F according to good- and \textit{ok-}match pairs. S denotes Simian and N denotes NiCad tool.}
%	\label{tab:good_classification}
%	\small
%	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
%		\hline 
%		Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
%		\hline
%		\hline
%		\multicolumn{9}{|c|}{good-match pairs} \\
%		\hline
%		S$_{df}$--N$_{df}$   & 1 & 0 & 1 & 0 & 1 & 4 & 0 & 7 \\
%		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   & 1 & 0 & 0 & 3 & 14 & 1 & 1 & 20 \\
%		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   & 0 & 0 & 3 & 0 & 7 & 0 & 0 & 10 \\
%		S$_{\textrm{\textit{EvCl}}}$--N$_{\textrm{\textit{EvCl}}}$   & 0 & 0 & 1 & 0 & 20 & 0 & 2188 & 2228 \\
%		\hline
%		Total   &   2   &   0   &  2   &  6   &   26   &   10   & 1320  & 1366 \\
%		Total (unique)  &   1   &   0   &  1   &  3   &   26   &   6   & 1320  & 1352 \\
%		\hline
%		\hline 
%%		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
%%		\hline
%		\multicolumn{9}{|c|}{ok-match pairs} \\
%		\hline
%		S$_{df}$--N$_{df}$        & 3 	& 0 	& 12	& 6 	& 3755  & 8	& 7  &  3791 \\
%		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   	& 8 	& 0 	& 28	& 4	& 904 & 29  & 32 &  1005 \\
%		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   	& 0 	& 0 	& 0 	& 0 	 & 29 	  & 0 		& 24 	& 53 \\
%		\hline
%		Total   &   11  &   0   &  32   &  10   &   712   &   30   & 63  & 858 \\
%		Total (unique)  &   8  &   0   &  23   &  8   &  480  &  28  & 61  & 608 \\
%		\hline
%	\end{tabular} 
%\end{table}

@@

\begin{table}
	\centering
	\caption{Statistics of non agreement-based clone pairs (Simian$_{df}$ and NiCad$_{df}$).}
	\label{tab:classification_indv_stats}
	\small
	\begin{tabular}{l|r|r|r|r}
		\hline 
		Tool & Clone pairs & ok-pairs & filtered & remaining \\ 
		%\hline 
		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
		\hline
		\multirow{1}{*}{\textit{Simian$_{df}$}} & 18422 & 140 & 17490 & 792 \\
		\hline
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-1} & 7040  & 226 & 6700 & 114 \\
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-2} & 22187  & 152 & 21990 & 45 \\
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 29227  & 378 & 28690 & 159 \\
		\hline
	\end{tabular} 
\end{table}

\subsubsection{Manual investigation of non agreement-based clone pairs}
%\subsubsection*{\textbf{Qualitas-\textit{O} (v. 2013-09-01r)}}
We performed manual investigation and classified the clone pairs reported by Simian$_{df}$ and NiCad$_{df}$ in the same way as the agreement-based clone pairs. The results of the manual investigation is reported in \Cref{tab:classification_good_o}.

%\subsection{Summary of true online clone pairs}
\begin{table}[H]
	\centering
	\caption{Numbers of true positive online clone pairs found by manual investigation}
	\label{tab:classification_true_pairs_summary}
	\small
	\begin{tabular}{l|r|r|r|r|r}
		\hline 
		Tool & A & A' & B & C & Total \\
		\hline
		good-pairs & 1 & 0 & 4 & 3 & 8 \\
		ok-pairs & 8 & 0 & 33 & 8 & 49 \\
%		Simian$_{df}$ pairs-1 & 35 & 0 & 90 & 8 & 133 \\
%		Simian$_{df}$ pairs-2 & 36 & 0 & 229 & 3 & 268 \\
		Simian$_{df}$ pairs & 71 & 0 & 318 & 10 & 399 \\
%		NiCad$_{df}$ pairs & 4 & 0 & 5 & 0 & 9 \\
%		NiCad$_{df}$ pairs-2 & 0 & 0 & 10 & 0 & 10 \\
		NiCad$_{df}$ pairs & 4 & 0 & 15 & 0 & 19 \\
		\hline 
		Total & 84 & 0 & 370 & 21 & 476 \\
		\hline
	\end{tabular} 
\end{table}

>>>>

\subsection{Experimental Framework}
To answer the three research questions, an experimental framework is designed as depicted in \Cref{fig:exp_framework}. We process two datasets, Stack Overflow and open source projects from Qualitas corpus. Java code fragments are extracted from Stack Overflow posts using regular expressions. We pre-process Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection. Then, we deploy two clone detection tools, Simian \cite{simian} and NiCad \cite{Roy2008,Cordy}, to locate clones between the two datasets. Due to a technical limit of Simian and NiCad to scale to large datasets, we partition the input and run the tools multiple times. Each run is composed of the whole Stack Overflow data and a single Qualitas project. We repeat the process until we cover 111 projects.

@@

\subsubsection{Datasets}
\begin{table}
	\centering
	\caption{Stack Overflow and Qualitas datasets}
	\label{tab:datasets}
	\small
	\begin{tabular}{l|r|r}
		\hline 
		Dataset & No. of files & SLOC \\
		\hline
		Stack Overflow & 144,075 & 2,347,269 \\ 
		\hline 
		Qualitas &  160,937 & 19,086,883 \\ 
		\hline 
	\end{tabular} 
\end{table}

@@

\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas} \cite{QualitasCorpus}. It is a curated Java corpus that has been used in several software engineering studies \cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The projects in the corpus represent various domains of software systems ranging from programming language to 3D and visualisation \cite{QualitasCorpus}. We selected the 20130901r snapshot of Qualitas corpus containing 112 Java open source projects. This release contains projects with releases no later than 1st September 2013. We chose a snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow. The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment, January--December 2016. The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow. Out of 112 Qualitas projects, there is one project, \textit{jre}, that does not contain Java source code so it is removed from the study. This results in totally 111 projects analysed in the study. As shown in \Cref{tab:datasets}, the 111 Qualitas project have 160,937 Java files containing 19,086,883 lines of code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

@@

\begin{table}
	\centering
	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian and NiCad}
	\label{tab:raw_stats}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\
			\hline
			Snippets & 1,086 & 1,530 & 1,240 & 12,886 \\
			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,372,599 & 229,176 & 206,760,077 \\
			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,447 & 185 & 16,047 \\
			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.64 & 5.32 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 29\% & 28\% & 25\% & 21\% \\
			\hline
		\end{tabular} %
	}
\end{table}

@@

\begin{table}
	\centering
	\caption{No.~of projects in Qualitas successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{l|r|r|r|r}
		\hline
		& Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$  & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ 
		\hline
		\textit{Successful} & 111 & 111 & 105 & 84 \\ 
		\textit{Clust.~fail} & -- & -- & 6 & 16 \\
		\textit{Renm.~fail} & -- &  -- & -- & 11 \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}[H]
	\centering
	\caption{Distribution of agreement-based clone pairs using Bellon's criteria for \textit{df} and \textit{EvCl} settings}
	\label{t_agreed_good_clone_pairs}
	\small
	\begin{tabular}{l|l|r|r}
		\hline
		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c}{No.~of clone pairs} \\
		\hline
		Simian & NiCad & good-match & ok-match \\
		%\hline
		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvCl}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvCl}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		\textit{df} & \textit{df} & 10 	& 9062 \\ 
		\textit{df} & \textit{EvCl} 	& 26 	& 1017 \\ 
		\textit{EvCl} 	& \textit{df} 	& 10 	& 88 \\
		\textit{EvCl} 	& \textit{EvCl} 	& 2228 & 19777 \\ 
		\hline
		\multicolumn{2}{l|}{Total} & 2274 & 29944 \\
		\hline
		\multicolumn{2}{l|}{Total (unique)} & 2261 &  29091 \\
		\hline
	\end{tabular}
\end{table}

\begin{figure*}
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{venn4_pairs_good_pt1+2}
		\caption{Distributions of good-match(0.7) pairs}
		\label{fig:venn4_orig_good}
	\end{minipage}
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{venn4_pairs_ok_pt1+2+3}
		\caption{Distributions of ok-match(0.7) pairs}
		\label{fig:venn4_orig_ok}
	\end{minipage}
\end{figure*}

@@

\begin{table*}
	\centering
	\caption{Classification results of agreement-based and non agreement-based clone pairs. S$_u$ denotes a number of unique Stack Overflow snippets. Q$_u$ and Q$_{up}$ denote a number of unique Qualitas Java files and unique Qualitas projects respectively.}
	\label{tab:classification_good_o}
	\small
	\resizebox{2.1\columnwidth}{!}{%
	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
		\hline
		Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
		\hline 
		\hline
		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 29  & 10 & \textbf{47} & 12 & 14 & 10 & 9158 & 35 & 82 & \textbf{9275} & 100 & 204 & 30 & \textbf{9322} & 112 & 218 & 35 \\
		\hline 
		\hline 
		\multirow{1}{*}{\textit{Simian$_{df}$}} & 80 & 0 & 336 & 16 & \textbf{432} & 148 & 229 & 38 & 209 & 63 & 167 & \textbf{439} & 136 & 214 & 49 & \textbf{871} & 271 & 428 & 58 \\
		\hline
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 8  & 0 & 27 & 1 & \textbf{36} & 16 & 15 & 5 & 77 & 3 & 82 & \textbf{132} & 52 & 55 & 17 & \textbf{168} & 67 & 69 & 19 \\ 
		\hline
	\end{tabular} 
	}
\end{table*}

@@

\begin{table}
	\centering
	\caption{Statistics of non-agreed clone pairs (Simian$_{df}$ and NiCad$_{df}$).}
	\label{tab:classification_indv_stats}
	\small
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|p{2.4cm}|r|r|r}
		\hline 
		Tool & Filter & C$_{\textrm{\textit{pairs}}}$ & good/ok & remaining \\ 
		%\hline 
		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
		\hline
		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline + reg.~expressions & 67570 & 2546 & 871 \\ %140 + 1482 + 926
		\hline
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-1} & 7040  & 226 & 6700 & 114 \\
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-2} & 22187  & 152 & 21990 & 45 \\
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & $similarity \geq 80\%$ & 229176  & 450 & 168 \\
		\hline
	\end{tabular} %
	}
\end{table}

\subsubsection{Manual investigation of non-agreed clone pairs}
%\subsubsection*{\textbf{Qualitas-\textit{O} (v. 2013-09-01r)}}
We performed manual investigation and classified the clone pairs reported by Simian$_{df}$ and NiCad$_{df}$ in the same way as the agreement-based clone pairs. The results of the manual investigation is reported in \Cref{tab:classification_good_o}.

%\subsection{Summary of true online clone pairs}
\begin{table}[H]
	\centering
	\caption{Numbers of true positive online clone pairs found by manual investigation}
	\label{tab:classification_true_pairs_summary}
	\small
	\begin{tabular}{l|r|r|r|r|r}
		\hline 
		Tool & A & A' & B & C & Total \\
		\hline
		good-pairs & 1 & 0 & 4 & 3 & 8 \\
		ok-pairs & 8 & 0 & 29 & 10 & 47 \\
		Simian$_{df}$ pairs & 80 & 0 & 336 & 16 & 432 \\
		NiCad$_{df}$ pairs & 8 & 0 & 27 & 1 & 36 \\
		\hline 
		Total & 97 & 0 & 396 & 30 & 523 \\
		\hline
	\end{tabular} 
\end{table}
